%-------------------------
% Resume in Latex
% Original Author : Sourabh Bajaj
% Current Author : Reid Cooper
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://me.reidcooper.dev/}{\Large Reid Cooper}} & Email : \href{mailto:reid.cooper8@gmail.com}{reid.cooper8@gmail.com}\\
  \href{https://me.reidcooper.dev}{https://me.reidcooper.dev} & Mobile : \href{tel:PHONE_PLACEHOLDER}{PHONE_PLACEHOLDER} \\
\end{tabular*}


%-----------SUMMARY-----------------
\section{Summary}
\small{Staff Engineer with 11+ years of Ruby on Rails and 3 years of Golang, specializing in microservice architecture, distributed systems, and platform reliability. Known for leading high-stakes engineering initiatives that deliver measurable business outcomes -- \$6M+ in new ARR, \$500k in annual cost savings, and 20\% reduction in logo churn. Scales engineering culture through guilds, mentorship, and AI enablement across cross-functional teams at scale.}
\vspace{4pt}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Teachable}{New York, NY · Mar 2019 -- Present · 7 yrs}
      {Staff Engineer}{1 yr}
      \resumeItemListStart
        \resumeItem{B2B Product Team Lead}
          {Led a 5-engineer team delivering Teachable's B2B offering from zero to production under a strict end-of-November deadline. Drove end-to-end ownership: product engineering roadmap, system architecture, cross-functional project facilitation, and technical mentorship -- conducting architecture and design reviews, mitigating risk, and empowering independent technical judgment. Delivered on time in November 2025 -- a 0-to-production effort in 3 months -- driving 115 beta schools onboarded (150+ on waitlist), 2,060 students enrolled with 100\% growth in 2 weeks, and a Q1 closed sale.}
        \resumeItem{File Migration Tiger Team}
          {Led a 5-engineer tiger team migrating all Teachable-hosted files and content away from Filestack under a strict 9-week deadline. Designed migration scripts spanning 5 repositories -- covering 30M+ database record updates across 45+ table/column pairs, integrity validation, rich text parsing, and consistent upload patterns across 56+ locations. Established best practices for large-dataset migrations and monadic patterns for procedural code reliability, reinforced through pairing sessions and code reviews -- enabling engineers to execute independently. Successfully migrated 15 million files on time, saving approximately \$500k per year.}
        \resumeItem{Platform Reliability \& Reporting}
          {Architected improvements to Teachable's user reporting and export platform to address reliability and scale concerns for large datasets. Authored Apache Airflow ETL pipelines and managed AWS DMS change data capture configurations to enrich the platform's data footprint. Built a Golang microservice integrating with an internal data warehouse's streaming service to deliver enriched datasets as NDJSON -- establishing a real-time data exposure layer within the Teachable product.}
        \resumeItem{Services Guild}
          {As Guild Co-Lead, facilitated cross-team sessions spanning microservice design, architectural decision-making, and AI enablement -- shaping how the engineering organization approaches AI as a discipline. Ran workshops on getting started, defining effective usage, context management, and incremental value -- creating space for engineers to surface struggles, identify problems to solve with AI, and explore hands-on.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Senior Software Engineer II; Growth Revenue}{2 yrs}
      \resumeItemListStart
        \resumeItem{Plan Service Adoption}
          {With senior leadership support, led an initiative for all product engineering teams to migrate their domains to a centralized school capabilities service -- decoupling the platform from hard-coded plan names and establishing a flexible foundation for future subscription tiers. Authored technical and product documentation -- covering migration patterns, risk areas, and definition of done -- and held open pairing sessions with engineers across teams, enabling each to lead their own domain migrations. Spanned 150+ locations across 3 applications; teams completed migrations in as little as 2 weeks -- drove a 21\% revenue increase, generating +\$6M in new ARR.}
        \resumeItem{Revenue Initiatives}
          {Introduced two new revenue streams: Plan Addons and Captions -- together generating \$350K in new revenue over 2 years. Designed and implemented both using state machine and monadic patterns for reliability, recoverability, and ease of maintenance -- Plan Addons spanning two services.}
        \resumeItem{School Capabilities Service}
          {Designed and built Teachable's first Golang microservice, achieving an average 2ms response time and 27k+ requests per minute -- the second-highest throughput application in the stack. Integrated with Chargebee for structured, consistent school plan management across the platform.}
        \resumeItem{School Deactivation}
          {Co-designed a platform-wide pattern to deactivate schools and all related dependencies and associations consistently across Teachable's services, resulting in a 20\% reduction in logo churn.}
        \resumeItem{Services Guild}
          {Founded Teachable's Services Guild and facilitated sessions on service design, domain-driven design, and architectural trade-offs -- growing technical culture across the engineering team. Produced a reference microservice template enabling engineers to go from zero to production using Hotmart's infrastructure tooling, and led the creation of 5+ microservices across the team.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Senior Software Engineer I; Student Experience Team Lead}{2.5 yrs}
      \resumeItemListStart
        \resumeItem{Video Platform Migration}
          {Led the full lifecycle of Teachable's student video platform migration from Wistia to Hotmart's in-house video player -- redesigning integrations across 5+ products, maintaining full course compliance system integrity, and executing the end-to-end migration of 8 million video assets, reducing video hosting costs from \$3M to \$1M annually.}
        \resumeItem{Team \& Guild Lead}
          {Served as Team Lead and Backend Guild Lead, mentoring engineers and driving cross-team platform initiatives and dependency upgrades across the engineering organization.}
        \resumeItem{On-Call Operability}
          {Co-led Teachable's On-Call Operability program; built and maintained processes for alerting, engineer readiness, and playbook design, and hosted simulated incidents to train and prepare the engineering organization.}
        \resumeItem{Page Generation Microservice}
          {Designed and built a microservice for server-side page generation, precompiling user-data-enriched page templates ready for consumption by a monorepo frontend package.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Software Engineer; Core}{1.5 yrs}
      \resumeItemListStart
        \resumeItem{Page Editor v2}
          {Designed and built Page Editor v2, replacing the legacy school page builder with an extensible content creation toolkit -- including new page-building capabilities and a managed data migration path for existing users.}
      \resumeItemListEnd

    \resumeSubheading
      {Mack Weldon}{New York, NY · Sept 2015 -- Mar 2019 · 3.5 yrs}
      {Full Stack Software Engineer}{}
      \resumeItemListStart
        \resumeItem{Loyalty Program}
          {Custom product solution designed and developed for Mack Weldon's first loyalty program, Weldon Blue. A rule based engine that offered tiered-based benefits to our customers before checkout.}
        \resumeItem{Data Warehouse}
          {Built first revision of Mack Weldon's founding data warehouse. Built using AWS Redshift, Data Pipelines, and SegmentIO. Streamed data from marketing, core e-commerce, and merchandise inventory platforms.}
        \resumeItem{Shopify POS System}
          {Designed and developed message broker integration using RabbitMQ to link core e-commerce platform with Shopify's POS system to help launch Mack Weldon's first store location in Hudson Yards, NYC.}
        \resumeItem{Peanut Butter and Jelly (PBJ)}
          {CMS Application that expedited content creation, landing, and platform pages. Reduced our workload roughly 70\%. Integration with Contentful CMS. Deployed and hosted on AWS S3.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------APPS-----------------
\section{Apps}
  \resumeSubHeadingListStart
    \resumeSubItem{Dashcoop}
      {Highly customizable Roku screensaver displaying real-time weather and clock data, available since 2018. Ruby/Sinatra backend integrating WeatherAPI and Google Geocoding. 9,300+ cumulative downloads.}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Monmouth University}{West Long Branch, NJ}
      {Master's of Science, Software Engineering;  GPA: 3.97}{}
    \resumeSubheading
      {Monmouth University}{West Long Branch, NJ}
      {Bachelor of Science, Software Engineering; Minor in Mathematics; GPA: 3.44}{}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{\textbf{Languages}{: Ruby/Rails (11 yrs), Golang (3 yrs), JavaScript, HTML/CSS, SQL, BrightScript}}
    \item{\textbf{Technologies}{: Microservice Architecture, AWS, Kubernetes, Docker, Terraform, PostgreSQL, Redis, Datadog, System Design, Performance \& Observability}}
    \item{\textbf{Core Skills}{: Technical Strategy, Cross-Functional Leadership, Organizational Influence, Stakeholder Communication, Incident Command, Mentoring}}
    \item{\textbf{AI Tools}{: GitHub Copilot, Claude, ChatGPT}}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
